---
title: "ANOVA for Top 6"
date: "August 17, 2015"
output: 
  html_document: 
    fig_caption: yes
    number_sections: no
    theme: spacelab
    toc: no
---
```{r, echo=FALSE, results="hide", error=FALSE, warning=FALSE, message=FALSE}
library(knitr)
library(ggplot2)
library(GGally)
library(DT)
library(ez)

source("../serca.R")

set_os_locales()
```

[Back to Overview](overview.html)


## ANOVA for Top 6
```{r AnovaTop6, echo=FALSE, cache=TRUE, warning=FALSE}

frequencies <- tbl_df(read.delim('../data/frequencies.txt', stringsAsFactors = TRUE, fileEncoding="UTF-8"))
t <- frequencies %>% 
    filter(Rank <= 6) %>%
    group_by(Label, Target) %>%
    filter(row_number() <= 6) %>%
    mutate(RowNo = row_number()) %>%
    ungroup() %>%
    arrange(Target, Label, desc(Probability)) %>%
    select(RowNo, Label, Target, Probability)

t <- t %>% group_by(Label, Target)

t$RowNo <- factor(t$RowNo)
t$Label <- factor(t$Label)
t$Target <- factor(t$Target)
#t$Wid <- factor(t$Wid)
#a <- ezANOVA(data=as.data.frame(t),dv=Probability, wid=.(Wid), within =.(RowNo), between = .(Label), detailed=F, type = 3)

a <- aov(formula = Probability ~ RowNo + Label + (RowNo * Label), data = t)
print(formula(a))
print(summary(a))

top.1 <- top.1 %>% mutate(Rank=1)
top.2 <-top.2 %>% mutate(Rank=2)
top.3 <-top.3 %>% mutate(Rank=3)
top.4 <-top.4 %>% mutate(Rank=4)

tops <- rbind(top.1, top.2, top.3, top.4)
tops <- tops %>% gather(Set, Probability, -Rank)
levels(tops$Set) <- list(TS="tem", Lab="umi", Online="onl")
tci <- function(x) {t.test(x, na.action=na.omit)$conf.int}
means <- tops %>% group_by(Set, Rank) %>% summarise(Mean=mean(Probability, na.rm=TRUE), CiLo=tci(Probability)[1], CiUp=tci(Probability)[1])

pd = position_dodge(width=0.5)
maxlim <- ceiling(max(means$CiUp)*10)/10
ggplot(data = means, aes(x = Rank, y = Mean, group = Set)) +
  geom_point(aes(shape=Set, fill=Set, ymax=maxlim), size=4, position=pd) +
  scale_shape_manual(values=c(24,24, 19)) +
  scale_fill_manual(values=c("black", "white", "black")) +
  theme_bw() +
  theme(plot.title=element_text(face="bold", size=14), panel.grid.major=element_blank(), panel.grid.minor=element_blank()) +
  ggtitle('Probability of response by rank, correlated across data sets')

  
```


c1 <- cor(top.1, use="complete")
c2 <- cor(top.2, use="complete")
c3 <- cor(top.3, use="complete")
c4 <- cor(top.4, use="complete")

key.cors <- function(x) {
  rn <- rownames(x)
  cn <- colnames(x)
  kc <- c(x[1,2], x[1,3], x[3,2])
  names(kc) <- c(paste(rn[1], cn[2], sep='-'), paste(rn[1], cn[3], sep='-'), paste(rn[3], cn[2], sep='-'))
  return(kc)
}

m1 <- key.cors(c1)
m2 <- key.cors(c2)
m3 <- key.cors(c3)
m4 <- key.cors(c4)

#top.1 <- top.1 %>% mutate(Rank=1)
#top.2 <-top.2 %>% mutate(Rank=2)
#top.3 <-top.3 %>% mutate(Rank=3)
#top.4 <-top.4 %>% mutate(Rank=4)

tops <- rbind(top.1, top.2, top.3, top.4)
tops <- tops %>% gather(Set, Probability, -Rank)
levels(tops$Set) <- list(TS="tem", Lab="umi", Online="onl")
tci <- function(x) {t.test(x, na.action=na.omit)$conf.int}

means <- tops %>% group_by(Set, Rank) %>% summarise(Mean=mean(Probability, na.rm=TRUE), CiLo=tci(Probability)[1], CiUp=tci(Probability)[1])

pd = position_dodge(width=0.5)
maxlim <- ceiling(max(means$CiUp)*10)/10
ggplot(data = means, aes(x = Rank, y = Mean, group = Set)) +
  geom_point(aes(shape=Set, fill=Set, ymax=maxlim), size=4, position=pd) +
  scale_shape_manual(values=c(24,24, 19)) +
  scale_fill_manual(values=c("black", "white", "black")) +
  theme_bw() +
  theme(plot.title=element_text(face="bold", size=14), panel.grid.major=element_blank(), panel.grid.minor=element_blank()) +
  ggtitle('Probability of response by rank, correlated across data sets')

[Back to Overview](overview.html)
