---
title: "Heterogeneity of Responses"
date: "August 21, 2015"
output: 
  html_document: 
    fig_caption: yes
    theme: spacelab
    toc: yes
---
```{r, echo=FALSE, results="hide", error=FALSE, warning=FALSE, message=FALSE}
library(knitr)
library(ggplot2)
library(GGally)
library(DT)
library(ez)
library(dplyr)
library(pastecs)
library(multcomp)

source("../serca.R")

set_os_locales()




[Back to Overview](overview.html)

```{r FreqHeteroInit, echo=FALSE, cache=TRUE}
frequencies <- tbl_df(read.delim('../data/frequencies.txt', stringsAsFactors = TRUE, fileEncoding="UTF-8"))
H <- frequencies %>% filter(Assoc != '?' & n > 1) %>% group_by(Label, Target) %>% summarise(H=-round(sum(Probability*log2(Probability)), 2))
H.spread <- H %>% select(Label, Target, H) %>% spread(Label, H)
```

## Heterogeneity of responses
As per De Deyne, Navarro, and Storms, 2013. Values filtered from blank &  idiosyncratic.

### Descriptives
```{r HeteroDesc, echo=FALSE, cache=TRUE}
kable(stat.desc(H.spread) %>% select(-Target), digits = 2)
```

### Individual values
```{r HeteroVals, echo=FALSE}
#DT::datatable(H.spread)
```

### ANOVA
```{r FreqHeteroA, echo=FALSE, cache=TRUE}
anova.H <- aov(H ~ Set, H)
print(formula(anova.H))
print(summary(anova.H))
print(c("Omega square:", round(omega_sq(anova.H), 2)))
ah.tuk <- glht(anova.H, linfct = mcp(Set="Tukey"))
ah.ci <- confint(ah.tuk)
gplot(ah.ci, aes(lhs, estimate)) + geom_linerange(aes(ymin = lwr, ymax=upr), data=ah.ci) + geom_point(aes(size=p), data=summary(ah.tuk)) + geom_point(shape=4, size=6) + geom_errorbar(aes(ymin=lwr, ymax=upr), width=0.25, data=ah.ci) + scale_size(trans="reverse") + geom_hline(linetype="dashed") +  theme_bw() + xlab("Data Sets") + ylab("Estimated mean difference") +
    theme(plot.title=element_text(face="bold", size=14), panel.grid.major=element_blank(), panel.grid.minor=element_blank()) + ggtitle('Multiple comparisons of mean heterogeneity') + coord_flip() + theme(aspect.ratio=240/640)

```

## Correlation
```{r FreqHetero, echo=FALSE, cache=FALSE}
kable(H.spread %>% select(umi, onl, tem) %>% cor, digits=2)

H <-  H %>% rename(Set=Label)
levels(H$Set) <- list(`TS`="tem", `Lab`="umi", `Online`="onl")

p <- ggplot(data=H, aes(x=H, group=Set)) +  scale_linetype_discrete()+ geom_line(stat="density", adjust=2.0, na.rm = TRUE, aes(linetype=Set, y=..count..), fill=NA) + theme_bw() + theme(plot.title=element_text(face="bold", size=14), panel.grid.major=element_blank(), panel.grid.minor=element_blank()) + ggtitle('Frequencies of response heterogeneity') + +theme(aspect.ratio=240/640)


```

[Back to Overview](overview.html)
